High-Performance Language Primitives for Distributed Architectures using Asynchronous Events

### 2012-11-04 doc/llr-pldi2013/related.tex
First commit on new low-level runtime paper for pldi

The Threaded Abstract Machine (TAM) is a programming model designed to
make it easy to port dataflow programs onto a parallel machine\cite{CullerGSvE93}.  
Conceptually our interface is similar to the dataflow languages TAM supported.
However, the implementation of TAM is designed for a class of much smaller machines
and therefore is based on much heavier communication and threading mechanisms.
While TAM supports composable asynchronous computation and communication, its
synchronization mechanisms still require blocking operations.

>>>>

The Threaded Abstract Machine (TAM) is a programming model designed to
make it easy to port dataflow programs onto a parallel machine\cite{CullerGSvE93}.  
Conceptually our interface is similar to the dataflow languages TAM supported.
However, the implementation of TAM is designed for a class of much smaller machines
and therefore is based on heavier communication and threading mechanisms.
While TAM supports composable asynchronous computation and communication, its
synchronization mechanisms still require blocking operations.
